\subsection*{What We Found}
\begin{itemize}
  \item Under a real-world deployment scenario (single fixed split, normalisation fitted on training data only, results averaged across five seeds), all three DL models achieve ADR in the 0.57--0.68 range, above chance but well below operationally useful levels. No architecture is a clear winner.
  \item With only five seeds the BiGRU shows ADR variance of $\pm 0.131$;
        LOTO cross-validation provides more stable per-device estimates
        (mean ADR \bigruLOTOadrMean, mean EER \bigruLOTOeerMean).
  \item Dataset size is the primary performance bottleneck: each binary
        classifier in trial\_1 trains on $\approx$52 windowed samples,
        far below what DL models typically require to generalise reliably.
\end{itemize}

\subsection*{Contributions}
\begin{itemize}
  \item \textbf{DL evaluation under real-world conditions.} Evaluated MLP, GRU, and BiGRU architectures on this dataset under a group-aware, transient-aware protocol that reflects what a practitioner would encounter when deploying the system: the model is trained once and applied to new transmissions without post-hoc selection.
  \item \textbf{Uncertainty quantification.} Results are averaged across five random seeds and supplemented with LOTO cross-validation, providing a rigorous estimate of the variance a deployed system would exhibit.
  \item \textbf{Data-efficiency result.} Demonstrated that sliding-window augmentation enables DL training with 10$\times$ fewer recordings by exploiting the full transient duration, confirming that device-discriminating hardware imperfections persist well beyond the initial signal segment used by the original pipeline.
  \item \textbf{Multi-class probe.} Showed that a single BiGRU trained on all 12 devices reaches \mcAccuracy{} accuracy (vs.\ \mcRandomBaseline{} random), confirming that discriminative information exists across all devices and that architecture is not the limiting factor while dataset size is (Appendix~\ref{app:multiclass}).
\end{itemize}

\subsection*{Future Directions}
\begin{itemize}
  \item Collect additional independent transients per device to push ADR toward
        operationally useful levels.
  \item Evaluate AND-aggregation at system level to reduce the high False Accept
        Rate under OR-aggregation.
  \item Explore per-device classifier ensembles: training multiple models per
        authorized device and combining their outputs via soft voting could
        reduce the high seed-to-seed variance observed in this work and yield
        more stable authentication decisions without architectural changes.
  \item Conduct adversarial robustness evaluation (white-box and black-box
        attacks on raw IQ waveforms), now that a rigorous unattacked baseline
        is established.
\end{itemize}
